Symmetry-based constraints on the size of the dynamical Solar neighborhood

### 2019-04-09 paper/ms.tex
Move Jz hist fig up earlier, add extra panel

We now repeat the same procedure for systematic offsets between $0$ and
$500\,\pc$ in the $z$ and $x$ components. In
Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth{} minus 5\uth{}
percentile divided by the true action value for the three different fiducial
orbits in Table \ref{tab:orbits}. The thick-disk (\thickcolor) orbit is the
one from Figure~\ref{fig:one_orbit_wrong_ref}, but we also now consider the
effect on the action determined for the thin-disk (\thincolor) and halo
(\halocolor) orbits.

@@

To further understand the effect of the midplane error, we also plot the
fractional error in $J_z$ as a function of $J_z$ for $z$ offsets of $10, 50,
100\,\pc$ (red, cyan, green, respectively) in Figure~\ref{fig:dJz_fun_Jz}. For
a thin disk-like orbit ($J_z\sim0.5\,\actunit$), even a $10\,\pc$ offset in
$z$ is enough to induce a $\sim50\%$ error in $J_z$. For larger values of
$J_z$, the fractional errors are suppressed, with the situation becoming worse
the greater the $z$ offset is.

In Figure~\ref{fig:Jz_hist} we plot a histogram of the observed values of
$J_z$ for the thick-disk orbit assuming a $z$ offset of $100\,\pc$ (i.e. the
{\em right} panel of Figure~\ref{fig:one_orbit_wrong_ref}). The true value of
$J_z$ is plotted as a vertical dashed line. Here we see that the spread in
$J_z$ induced by a systematic offset in $z$ is non-Gaussian and bimodal.
Furthermore, neither of the modes lie at the true value of $J_z$.

>>>>

In Figure~\ref{fig:Jz_hist} we plot a histogram of the observed values of
$J_z$ for the thick-disk orbit ({\em upper panel}) and thin-disk orbit ({\em
lower panel}) assuming a $z$ offset of $100\,\pc$ (i.e. the {\em right} panel
of Figure~\ref{fig:one_orbit_wrong_ref}). The true value of $J_z$ is plotted
as a vertical dashed line. Here we see that the spread in $J_z$ induced by a
systematic offset in $z$ is non-Gaussian and bimodal. Furthermore, neither of
the modes lie at the true value of $J_z$. In the case of the thin-disk orbit
({\em lower panel}), we see that, in addition to the prior complications, the
error distribution is not even centered on the true value. This comes about
when the midplane error is $\gtrsim z_{\text{max}}$, and can be understood by
realizing that in such a case the midplane offset always acts to increase the
value of $J_z$, resulting in a biased estimate of $J_z$.

Empirically describing the error distribution shown in
Figure~\ref{fig:Jz_hist} is difficult. Of course, Gaussian summary statistics
are not adequate. We therefore elect to measure this error by computing the
95\uth{} percentile minus the 5\uth{} percentile of the distribution of
observed action values. We refer to this quantity as $\Delta J_i$ for each
action value. Because of the bimodality of the error distribution, this
quantity roughly measures the distance between the peaks of the two modes.
Furthermore, this bimodality also implies that $\Delta J_i$ is not very
sensitive to the exact percentiles used. This summary statistic does not
reflect the bias induced when the midplane error is $\gtrsim z_{\text{max}}$.

We now repeat the same procedure as in Figure~\ref{fig:one_orbit_wrong_ref} but for systematic offsets between $0$ and
$500\,\pc$ in the $z$ and $x$ components. In
Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth{} minus 5\uth{}
percentile divided by the true action value for the three different fiducial
orbits in Table \ref{tab:orbits}. The thick-disk (\thickcolor) orbit is the
one from Figure~\ref{fig:one_orbit_wrong_ref}, but we also now consider the
effect on the action determined for the thin-disk (\thincolor) and halo
(\halocolor) orbits.

@@

To further understand the effect of the midplane error, we also plot the
fractional error in $J_z$ as a function of $J_z$ for $z$ offsets of $10, 50,
100\,\pc$ (red, cyan, green, respectively) in Figure~\ref{fig:dJz_fun_Jz}. For
a thin disk-like orbit ($J_z\sim0.5\,\actunit$), even a $10\,\pc$ offset in
$z$ is enough to induce a $\sim50\%$ error in $J_z$. For larger values of
$J_z$, the fractional errors are suppressed, but the induced error can still be large
depending on how great the $z$ offset is.
